\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Sandesh}{Vernekar}{ \urlstyle{same}\href{http://debarghyadas.com}
{DOB-02 Feb,2003} \href{http://fb.co/dd}{}\\
\href{mailto:deedy@fb.com}{sandeshvernekar213@gmail.com} | 9113033462| \href{mailto:dd367@cornell.edu}{LinkedIn-sandesh-vernekar}
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{10pt} % Adds 10pt of vertical space
\section{Education} 

\subsection{Visvesvaraya }
\subsection{Technological University}
\descript{BE in Information Science }
\descript{ and Engineering}
\location{Grad.May 2024}
\location{ CGPA: 7.56} 
\sectionsep

\subsection{SHRI MARIKAMBA }
\subsection{P.U. COLLEGE  | SIRSI}
\location{March 2020}
\location{ Percentage: 72.83} 
\sectionsep

\subsection{MARIKAMBA HIGH SCHOOL  }
\location{ April 2018 | Karnataka, Sirsi}
\location{ Percentage: 88.48}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{10pt} % Adds 10pt of vertical space
\section{Coursework}
\subsection{UNDERGRADUATE}
Data Structures & Algorithms \\
Design And Analysis of Algorithms \\
Object Oriented Programming \\
Operating System \\
Database Management System \\
Computer Networks \\

\sectionsep
\vspace{10pt} % Adds 10pt of vertical space

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Languages:}
\textbullet{} C \\
\textbullet{} Java \\
\textbullet{} HTML\\
\textbullet{} CSS\\


\location{Familiar:}
\textbullet{}C++ 
 \textbullet{} python
\textbullet{} MySQL \\

\location{Tools:}
\textbullet{} Figma
 \textbullet{} UiPath



\sectionsep
\vspace{10pt} % Adds 10pt of vertical space

\section{Qualifications}

\textbullet{}  Working under Pressure\\
\textbullet{}  Conflict resolution\\
\textbullet{} Communication\\
\textbullet{}  Emotional Intelligence\\


\sectionsep






%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    





\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{10pt} % Adds 10pt of vertical space

\section{Experience}
\runsubsection{Full Stack Web Development Intern }
\descript{|  Varcons Technologies Pvt. Ltd }
\location{March 13, 2023 - April 16, 2023}
\sectionsep


\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Completed Full Stack Web Development Internship, organized and handled by Varcons Technologies Pvt. Ltd.
\item Worked on the project titled "Template for Free Stock Photo and Video Site," creating fully-fledged functional web templates for a client.
\item Successfully met design briefs and client specifications outlined in the project proposal and Demonstrated strong design skills and maintained a self-motivated attitude towards learning.
\item Exceeded expectations and completed the project within the designated timeframe.
\end{tightemize}
\sectionsep




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\section{PROJECTS}


  \runsubsection{E-book Management System}
\descript{| mysql | php| html |css  }
\begin{tightemize}
\item Streamlined e-book purchasing: Developed an online platform enabling users to browse, purchase, and download e-books in PDF format, enhancing accessibility and convenience for readers.
\item Enhanced knowledge accessibility: Facilitated reading anytime, anywhere by providing a user-friendly e-book management system, eliminating the need for physical books and promoting a seamless learning experience.
\end{tightemize}
 \runsubsection{Template - Coursezz: Site to share Stock Photos}
 \descript{| html |  css  |   javascript }
\begin{tightemize}
\item Developed a simple website similar to platforms like Pexels or Shutterstock, showcasing copyright-free images and providing a library of stock images available for free download.

\end{tightemize}
\sectionsep

 \runsubsection{Automated Weather Bot}
\descript{| UiPath }
\begin{tightemize}
\item Leveraged UiPath's RPA capabilities to automate data extraction and processing tasks, including developing and implementing an Automated Weather Bot. The bot utilizes APIs and web scraping techniques to extract accurate and timely weather details from reliable sources.
\item Successfully completed the project, delivering a reliable Automated Weather Bot that gathers weather data from various sources and provides accurate information.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS



\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{10pt} % Adds 10pt of vertical space


\section{certifications} 
\vspace{10pt} % Adds 10pt of vertical space
\renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
\begin{tightemize}
\item \location{ Introduction to java -coursera} 
\item \location{ Introduction to Frontend  Development -coursera}  
\item \location{ Problem Solving(Basic)in C -HackerRank}  
\item \location{ Certificate of Internship-Varcons Technologies Pvt. Ltd} 




\end{tightemize}

\end{minipage} 
\end{document}  \documentclass[]{article}